\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{Assessing economic inequality with tax data - Switzerland from 1945 to 2010}

### 2014-06-30 paper/subdocuments/data.Rnw
updated summary table

\begin{table}[h]
\begin{tabular}{lcccc}
                                   & FTA       & Survey data\\
Statistical unit                   & individuals/couples  & households\\                                   
Concepts of economic ressources?   & limited   & yes (for recent periods)\\
Equivalisation?                    & limited   & yes\\
Top incomes covered?               & yes       & no\\
Low incomes covered?               & no        & yes\\
Range                              & 1945-2010 & 1982-2011\\
Comparison over time possible? 	   & yes       & limited\\
Cross country comparison possible? & limited   & yes

>>>>

\begin{table}[h]
\begin{tabular}{lcccc}
                                   & FTA       & Survey data\\
Statistical unit                   & Tax units (individuals/married couples)  & Households\\                                   
Concepts of economic resources  & Data-driven   & Theory-driven\\
Population coverage & total population & sample \\ 
Top incomes covered                 & Yes   & No\\
Low incomes covered?               & no        & yes\\
Comparison over time possible 	   & Long       & Short \\
Cross country comparison possible? & limited   & possible
